\chapter{Project Schedule Management}
In this section, we will elaborate on the subsequent activities that followed the development of the initial Gantt chart and Work Breakdown Structure (WBS). We will provide detailed information about the development team members and the milestones that have been established. Finally, we will present the final Gantt chart and the network diagram, illustrating the comprehensive planning and scheduling of the project.


\section{Project Team}
\begin{itemize}
    \item \textbf{Project Manager:} Tony Prince
    \item \textbf{Programmer/Analyst:} Karan Goel
    \item \textbf{Programmer/Analyst:} Banin Sensha Shrestha
\end{itemize}

\section{Project Milestones}
\begin{enumerate}
    \item \textbf{Project Kick-Off Milestone:}
    This marks the official start of the project, involving setting up and conducting the kick-off meeting. The agenda is prepared and all team members and stakeholders are notified and encouraged to understand their roles and responsibilities.
    
    \item \textbf{Planning Phase Completion Milestone:}
    Completion of the planning phase, including integration of data analysis tools, creation of the Work Breakdown Structure (WBS), survey preparation, requirements analysis, risk management planning, budget estimation, and project schedule development. This milestone transitions the project from planning to execution.
    
    \item \textbf{Budget Approval Milestone:}
    Achieved upon successful estimation and approval of the project budget, encompassing tasks such as budget estimation and securing necessary approvals.
    
    \item \textbf{Gantt Chart Creation Milestone:}
    Completion of the project scheduling phase with the creation of the Gantt chart, facilitating visual tracking of project activities and timelines.
    
    \item \textbf{Design Phase Completion Milestone:}
    Completion of the design phase, including the design of user interfaces and back-end systems, approval of Business Process Documents (BPD), and planning for hardware design and integration. This milestone prepares the project for a smooth transition to the development phase.
    
    \item \textbf{Execution Phase Completion Milestone:}
    Represents the end of the execution phase, with major tasks such as the implementation of system components like Recreation Programs Registration, Health-Management Classes Registration, Tracking System, Incentive System, and hardware installation completed.
    
    \item \textbf{Testing and Quality Assurance Milestone:}
    Focuses on ensuring the system's readiness and reliability before deployment, including all levels of testing (unit, integration, user) and resolution of any issues, preparing the system for go-live.
    
    \item \textbf{Monitoring and Promotion Milestone:}
    Beyond project completion, this milestone ensures the ongoing operation and promotion of the system, including system monitoring, addressing operational issues, gathering user feedback for continuous improvement, providing hyper-care support, and promotional activities to boost system usage among employees.
\end{enumerate}