\chapter{Project Integration Management}
Our first step in ensuring the successful delivery of this project for our client is to gain a comprehensive understanding of their primary goals and objectives. This part provides an overview of the main objectives, initial proposals, and business case studies that have been developed in consultation with the client.

\section{Main Objectives}

Manage Your Health, Inc. (MYH) is a Fortune 500 company that provides a variety of healthcare 
services across the globe. MYH has more than 20,000 full-time employees and more than 5,000 part-time 
employees. The have recently updated their strategic plan with key goals include reducing internal costs, increasing 
cross-selling of products, and exploiting new Web-based technologies to help employees, customers, and 
suppliers. We have summarized the client's goals in Table \ref{tab:objectives}:

\begin{table}[h]
\centering
\begin{tabular}{|>{\bfseries}l|p{9cm}|}
    \hline
    \textbf{Objective} & \textbf{Description} \\
    \hline
    Business Costs Reduction & Reduce internal expenses to improve efficiency and profitability. \\
    \hline
    Business Growth & Expand market reach and revenue by increasing cross-selling opportunities. \\
    \hline
    Employees and Customer Growth & Foster better collaboration among employees, customers, and suppliers by using new web-based technologies, thereby improving the development and delivery of healthcare products and services. \\
    \hline
\end{tabular}
\caption{Client's Key Objectives}
\label{tab:objectives}
\end{table}

In response to these challenges, the client has presented three potential solutions and has requested us to conduct a preliminary analysis to determine which option best aligns with their needs:

\begin{enumerate}[label=\textbf{\arabic*.}]
    \item \textbf{Health Coverage Costs Business Model:} Develop a secure application to model and analyze healthcare expenses. Although this tool has an initial development cost of \$100,000, it is expected to save \$20 per full-time employee annually.

    \item \textbf{Web-Enhanced Communications System:} Create a web-based system to streamline product development and delivery. This system is projected to save \$2 million annually, with a development cost of \$3 million and annual maintenance expenses.

    \item \textbf{Recreation and Wellness Intranet Project:} Launch an intranet application to promote employee health and wellness. The project aims for net savings of \$30 per employee each year by reducing healthcare premiums through improved employee health.
\end{enumerate}

\section{Proposal Analysis}

As per the request stated by our client we did initial analysis to find the solution that will best fullfill their needs

\

\section{Business Case Study}